doe-pkgs-analysis

### 2021-09-10 analysis/doe-pkgs-analysis.Rmd
Test some visualisation by author.

---
title: "doe-pkgs-analysis"
author: "Dewi Lestari Amaliah - 31251587"
date: "15/08/2021"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(yaml)
library(reshape)
library(tidyverse)
library(lubridate)
library(splitstackshape)
library(igraph)
library(geomnet)
library(ggnetwork)
library(tidygraph)
library(ggraph)
library(networkD3)
library(plotly)
library(qdapRegex)
```

@@

```{r}
ggraph(routes_tidy, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point(aes(color = aut_gr)) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()

```

@@

# Interactive Plot

```{r}
nodes_d3 <- pkg_nodes %>%
  rowid_to_column("id") %>%
  mutate(id = id - 1)

edges_d3 <-routes_tidy %>%
  activate(edges) %>%
  data.frame() %>%
  mutate(from = from - 1,
         to = to - 1)

forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "L2", Group = "aut_gr", 
             opacity = 1, fontSize = 16, zoom = TRUE)
```

>>>>

---
title: "doe-pkgs-analysis"
author: "Dewi Lestari Amaliah - 31251587"
date: "15/08/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(yaml)
library(reshape)
library(tidyverse)
library(lubridate)
library(splitstackshape)
library(igraph)
library(geomnet)
library(ggnetwork)
library(tidygraph)
library(ggraph)
library(networkD3)
library(plotly)
library(qdapRegex)
library(shiny)
library(visNetwork)
```

@@

```{r}
ggraph(routes_tidy, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point(aes(color = aut_gr)) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()
```

```{r}
aut_tidy_1st_aut <- aut_tidy_join[!duplicated(aut_tidy_join$L2), ] %>%
  select(L2, author)

aut_gr <- aut_tidy_1st_aut %>%
  group_by(author) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  mutate(aut_gr = as.factor(ifelse(n > 1, author, "other")))

pkg_nodes_1aut <- left_join(aut_tidy_1st_aut, aut_gr, by = "author") %>%
  select(L2, aut_gr) %>%
  mutate(first_aut = factor(aut_gr, levels = c("Ulrike Groemping",
                                           "John Lawson",
                                           "Robert B. Gramacy",
                                           "Delphine Dupuy",
                                           "Ernesto Barrios",
                                           "Kevin Wright",
                                           "Peng Liu",
                                           "Shwetank Lall",
                                           "other"))) %>%
  select(L2, first_aut)

routes_igraph_1aut <- graph_from_data_frame(d = pkg_edges, vertices = pkg_nodes_1aut, directed = TRUE)

# create the input based on the igraph object
routes_tidy_1aut <- routes_igraph_1aut %>% as_tbl_graph() %>%
  activate(edges)

ggraph(routes_tidy_1aut, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point(aes(color = first_aut)) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()
```

@@

# Interactive Plot with visnetwork

```{r}
nodes_d3 <- pkg_nodes_1aut %>%
  rowid_to_column("id") %>%
  mutate(id = id - 1)

edges_d3 <-routes_tidy_1aut %>%
  activate(edges) %>%
  data.frame() %>%
  mutate(from = from - 1,
         to = to - 1)

forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "L2", Group = "first_aut", 
             opacity = 1, fontSize = 16, zoom = TRUE)
```

```{r}
# shinyApp(
#   ui = fluidPage(
#     selectInput("first_aut", "Choose the author:",
#                     choices = levels(pkg_nodes_1aut$first_aut)),
#       mainPanel(plotOutput(outputId = "net"))
#     ),
#   
#   server = function(input, output){
#     
#     dat <- reactive({
#       if (input$first_aut == "Ulrike Groemping"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Ulrike Groemping", "Ulrike Groemping", "Other")))
#       }
#       
#       if (input$first_aut == "John Lawson"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "John Lawson", "John Lawson", "Other")))
#       }
#       
#       if (input$first_aut == "Robert B. Gramacy"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Robert B. Gramacy", "Robert B. Gramacy", "Other")))
#       }
#       
#       if (input$first_aut == "Delphine Dupuy"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Delphine Dupuy", "Delphine Dupuy", "Other")))
#       }
#       
#       if (input$first_aut == "Ernesto Barrios"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Ernesto Barrios", "Ernesto Barrios", "Other")))
#       }
#       
#       if (input$first_aut == "Kevin Wright"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Kevin Wright", "Kevin Wright", "Other")))
#       }
#       
#        if (input$first_aut == "Peng Liu"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Peng Liu", "Peng Liu", "Other")))
#        }
#       
#       if (input$first_aut == "Shwetank Lall"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Shwetank Lall", "Shwetank Lall", "Other")))
#       }
#       
#       if (input$first_aut == "other"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "other", "Other authors", "Other with > 1 packages")))
#       }
#       
#       graph_from_data_frame(d = pkg_edges, vertices = aut, directed = TRUE) %>%
#         as_tbl_graph() %>% activate(edges)
#     })
#     
#     
# 
#     output$net <- renderPlot(
#       ggraph(dat, layout = "stress") +
#         geom_edge_link(aes(color = type),
#                        arrow = arrow(length = unit(2, 'mm')),
#                        end_cap = circle(1, 'mm')) +
#         geom_node_point(aes(color = author), size = 3) +
#         geom_node_text(aes(label = name), repel = TRUE, size = 3.5) +
#         scale_color_manual(values = c("black", "#6C3483")) +
#         theme_graph()
#     )
#   },
#   
#   options = list(height = 1500,
#                  width = 1500)
#   
# )
```
